Replication Survey

### 2023-08-18 docs/manuscript/manuscript.tex

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Definitions of Replication and its Epistemic Functions}
\begin{itemize}
    \item Respondents report thinking about replicability (73.9\%) talking with colleagues about replicability (65.0\%) and considering replicability when undertaking peer-review (59.0\%). 
    \item Far fewer respondents report attempting replications (31.8\%). 
\end{itemize}

\begin{itemize}
    \item Coded analysis of Q6
\end{itemize}

A majority of respondents believe replications can serve epistemic functions.
\begin{itemize}
    \item Q7 control of chance 64.5\%
    \item Q7 identify product of flawed design 59.7\%
    \item Q7 construct validity 75.2\%
    \item External validity population 62.9\%
    \item External validity location 67.8\%
    \item Human, Nature Society, and Qualitative researchers had lower agreement on each point.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Replication Attempts}
\begin{itemize}
    \item sub-set demographics
    \item Q18 - same location response to characterize the attempts
    \item Q19 - Motivations
    \item Q20-21 - Replication outcome to component accessibility comparison. Perhaps also a comparison of success across locations by field of study (depending on the numbers).
    \item From Q21f percent that published their findings. The into Q22 why didn't respondents pursue publication.
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Analytical Approach}

We conducted two statistical analyses of the survey responses.
First, we analyzed researcher perspectives on replicability by coding and calculating summary variables and statistics for three themes: how geographic researchers define replicability, factors researchers believe affect the chances of replicating a study, and factors researchers affect the decision to attempt to replicate a study.
Second, we analyzed researchers' experiences attempting to replicate prior studies.

\subsubsection*{Analyzing Researcher Perspectives on Reproducibility}

\noindent For our first set of analyses, we examined the full set of survey responses.

\textit{Defining Reproducibility:} 
We coded participants' qualitative definitions of ``reproducibility'' following two procedures.
First, we measured the similarity of each provided definition to the definition adopted by the \textcite{NASEM2019}. 
The NASEM defines reproducible research as having four characteristics --- same data, same procedure, same results, and same conditions.
To make this comparison, each of the authors independently coded each respondent definition for the presence/absence of each of the four characteristics included in the NASEM definition.
Disagreements in the assignment of codes were resolved through discussion between the three authors.
We created an aggregate measure of definition similarity for the final coded response for each participant by counting the presence of each NASEM definition characteristic, resulting in a measure with the domain [0, 4].

Second, we coded each definition to one of four motivations for ensuring the reproducibility of a study: (i) to facilitate the assessment of prior work, (ii) to assess experimental research, (iii) to improve transparency and facilitate further extension of work, and (iv) to improve the transparency and consistency of data collection.
We derived this coding from common themes in the responses and our own reading of the reproducibility literature.
As above, each definition was independently coded by each author before code assignments across authors were compared with disagreements resolved through discussion.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Definitions of Replication and its Epistemic Functions}
Geographic researchers are thinking about replicability and link the act of replicating a study to a number of different epistemological functions (Figure A). 
A majority of respondents reported thinking about replicability (74\%), talking with colleagues about replicability (65\%), and considering replicability when undertaking peer-review (59\%) during the past two years. 
Respondents believe that replication studies can be used to assess the construct validity of a prior study (75\%) and whether the claims of that study will hold in new locations (67\%) or new populations (63\%). 
While respondents clearly linked replication to these epistemological objectives, they were also more likely to agree than strongly agree that replications could meet these goals.
When compared to those working in other subfields, respondents that identified specializing in human geography or the study of nature and society were less likely to agree that replications could be used to achieve these goals. 
For example, while 87 percent of respondents specializing in GIScience and methods believe replications could be used to assess whether a claim was the product of chance, just 57 percent of human and nature-society researchers agreed with this statement.

\begin{center}
\textbf{Insert Figure A About Here}
\end{center}

However, when respondents provided their own definitions of replicability many of these same concepts were not explicitly included. 47 percent of respondents included the need to assess or improve how well a prior study as part of their definition of replicability. 19 percent of respondents included the motivation to externally validate the claims of the original study by repeating the methods with new data in a new context.

Rather than focusing on these larger concepts, most respondent definitions presented criteria that identify a replication.

Analysis of coded Q6. Coding explicit mentions of the three dimensions of the NASEM replicability definition
\begin{itemize}
    \item New Data - 12\%
    \item Same Method - 56\%
    \item Results same or similar - 65\%
    \item Only 7\% of respondents mention all three
\end{itemize}

Subfield variation
\begin{itemize}
    \item New Data - 12\%
    \item Same Method - 56\%
    \item Results same or similar - 65\%
    \item Only 7\% of respondents mention all three
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Replication Attempts}
Far fewer respondents report attempting replications (31.8\%).

\begin{itemize}
    \item sub-set demographics
    \item Q18 - same location response to characterize the attempts
    \item Q19 - Motivations
    \item Q20-21 - Replication outcome to component accessibility comparison. Perhaps also a comparison of success across locations by field of study (depending on the numbers).
    \item From Q21f percent that published their findings. The into Q22 why didn't respondents pursue publication.
\end{itemize}
